Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-01-02 automatica/paper.tex
removed sections related to Transient Performance Specifications
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\title{Safe and Robust Formal Synthesis of Digital Controllers
       for Continuous Plants with Transient Performance Specifications}
% Title, preferably not more
% than 10 words.

@@

%-------------------------------
\subsection{Notation} 
\label{ssec:notation}
%-------------------------------

\textcolor{red}{Elizabeth: we need to define the notation used throughout the paper.}

@@

%---------------janus----------------
\section{CEGIS of digital control system with transient specifications}
\label{sec:method}
%-------------------------------

%-------------------------------
\subsection{Synthesis in frequency domain}
\label{ssec:frequencycegis}
%-------------------------------

%-------------------------------
\subsection{Synthesis of state feedback controllers}
\label{ssec:sscegis}
%-------------------------------

%-------------------------------
\subsection{Synthesis of state observers}
\label{ssec:sobsvcegis}
%-------------------------------

>>>>

\title{Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants}
% Title, preferably not more
% than 10 words.

@@

@@
